Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
adding info to intro

Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and
Spectrum-Based Fault Localization (\sfl{}) are two very popular techniques that
leverage different principles to automate fault isolation. An example of a MBSD
is Dynamic Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} as well as some
work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927,Ko:2008:DRA:1368088.1368130},
a technique that traces back statements in the code that influence some point of
interest, such as the evaluation of a failing assertion. In contrast to \ds{},
\sfl{}~\cite{7390282} does not analyze code. Instead, it is a black-box,
statistical fault localization method that computes suspiciousness values
associated with program entities (e.g., methods) based on coverage information
gathered during the execution of test cases as well as the output of test cases.
More precisely, \sfl{} uses coverage information of passing and failing test
cases to identify likely faulty statements and produces on output a list of
program entities ranked in decreasing order of suspiciousness. \ds{} and \sfl{}
are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{} ranks
the relevant parts of the code.

%% Similarly to \ds{}, \sfl{} received
%% tremendous attention in research over the years,
%% but its applicability to support
%% debugging remains
%% questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
%% Despite the skepticism of the research community, \sfl{} has been
%% shown useful in supporting downstream analyses, such as Automated
%% Program Repair
%% (\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
%% an increasingly popular technique that looks for fixes to buggy
%% statements. Tools like JAFF \cite{arcuri-2011}, Prophet
%% \cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
%% and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
%% likely fixes.

>>>>

Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and
Spectrum-Based Fault Localization (\sfl{}) are two very popular techniques that
leverage different principles to automate fault isolation. An example of a MBSD
is Dynamic Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} as well as some
work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927,Ko:2008:DRA:1368088.1368130},
a technique that traces back statements in the code that influence some point of
interest, such as the evaluation of a failing assertion. On the one hand, similarly to \ds{},
\sfl{} received tremendous attention in research over the years, but its
applicability to support debugging remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
On the other hand, in contrast to \ds{},
\sfl{}~\cite{7390282} is instead a black-box,
statistical fault localization method that computes suspiciousness values
associated with program entities (e.g., methods) based on coverage information
gathered during the execution of test cases as well as the output of test cases.
More precisely, \sfl{} uses coverage information of passing and failing test
cases to identify likely faulty statements and produces on output a list of
program entities ranked in decreasing order of suspiciousness. \ds{} and \sfl{}
are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{} ranks
the relevant parts of the code.

%% Despite the skepticism of the research community, \sfl{} has been
%% shown useful in supporting downstream analyses, such as Automated
%% Program Repair
%% (\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
%% an increasingly popular technique that looks for fixes to buggy
%% statements. Tools like JAFF \cite{arcuri-2011}, Prophet
%% \cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
%% and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
%% likely fixes.
